### 2018-06-29 Thesis/Parts/Background/Background.tex
Feedback update

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Introduction and Background}
\subheader{Information retrieval}
Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. The most practical example of this is a search engine. Given one or more search words the search engine will attempt to find relevant information. For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information). To be able to do this, the search engine must know which texts are related. This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency. Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.

\subheader{Neural Network}
A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
Neural Networks are multi-layered computational software, based on matrix calculations, which tries to map input values to output values. This mapping uses a pre-defined amount of layers that modify the values through matrix calculations. Neural networks rely on training to create optimal values for these layers. The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks. Neural networks can be applied to many different tasks, as long as there is sufficient training data available. The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for all input and output sets.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The search engine searches for relevant information"}
\end{center}
the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information). This result in a matrix, a vector per word which is referred to as a word embedding. This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run. Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results. Therefore, word embeddings from different runs of the same neural network cannot be compared. Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.

\subheader{Embedding}
An embedding is a distributed, numerical representation of text in a vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized. This means that the same word trained in two separate runs do not have to have the same embedding. However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}. In the case of a word embedding, the embedding represents the word. These embeddings are created using machine learning models, which create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}. Once trained, the embeddings can be used to construct embeddings for collections of texts. For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings. The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.

\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

@@

\subsubheader{TF-IDF}
TF-IDF is an abbreviation for Term Frequency times Inverted Document Frequency. This method does not rely on a neural network and therefore does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences. The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word. This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score. The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size. If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary. Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence. This reduces the amount of storage needed when hashing is not applied. It furthermore reduces the number of words which occur rarely. Due to the nature of TF-IDF, these rare words have a high score, canceling out other more frequent words, while rarely occurring in the corpus.
\end{jumpin}

As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.

\subheader{Validation methods}
The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through, among others the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric} and, for classification tasks, the rank of the correct class, which is in this research a journal. The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization. These tasks can be designed to produce a score that indicates the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, findings about the performance of an embedding method are limited to the task on which they are tested. Their results cannot be generalized to state that the embeddings are overall "performing well". Validation tasks use either labeled or unlabeled data. Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data. Labeled data enables the use of unsupervised learning models since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration. Unlabelled data, on the other hand, requires human interaction to give a score for the produced result. The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.

@@

A classification validation method is a simple task which assigns a label to a text. \citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate. In their setup, the text was a pair of texts, and their categories were duplicate and non-duplicate. \citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie reviews. They validated their proposed paragraph vector model by determining whether a review was positive or negative.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings. The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain-specific embeddings are trained on a collection of texts that uses uncommon English (i.e., domain-specific terms) or is limited to a small number of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
\subheader{Research environment}
The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data. \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark. This allows for much tighter integration between relational and procedural processing. The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.
\subheader{Text properties}
\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language. Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model. This shows the relation between the word occurrences rank and the actual occurrences. This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Introduction and Background}
\subheader{Information retrieval}
Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. 
\\\\The most practical example of this is a search engine. Given one or more search words the search engine will attempt to find relevant information. For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information). To be able to do this, the search engine must know which texts are related. \\\\This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency. Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.

\subheader{Neural Network}
A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values. This mapping uses a pre-defined amount of layers that modify the values through matrix transformations. Neural networks rely on training to create optimal values for these layers. The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks. Neural networks can be applied to many different tasks, as long as there is sufficient training data available. The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for all input and output sets, without under performing on other sets\footnote{Having only good results for the training/validation set is know as overfitting. This means that the layer-values are fine-tuned to only perform (extremely) well on one set, while under performing on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The quick brown fox jumps over the lazy dog"}
\end{center}
the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog). It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog). This result in a matrix, a vector per word which is referred to as a word embedding. This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run. Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results. Therefore, word embeddings from different runs of the same neural network cannot be compared.

\subheader{Embedding}
An embedding is a distributed, numerical representation of text in a multi-dimensional vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized. This means that the same word trained in two separate runs do not have to have the same embedding. However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}. In the case of a word embeddings, the embeddings represent the words. These embeddings are created using machine learning models, which do not have the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}. Once trained, the embeddings can also be used to construct embeddings for collections of texts. For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings. The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. This is illustrated in figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
\begin{figure}[hbt]
\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}}\label{figure:word2vecModels}
\end{figure}
\FloatBarrier
\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

@@

\subsubheader{TF-IDF}
Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and, therefore, does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. Figure~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation. The multiplication of the TF and IDF is referred to as the TF-IDF score. The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word. This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score. The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size. If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.  The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences. Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence. This reduces the amount of storage needed when hashing is not applied. It furthermore reduces the number of words which occur rarely. Due to the nature of TF-IDF, these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
\vspace{0.3in}\begin{table}[hbt]
\begin{center}
\begin{tabular}{|p{1in}|p{1in}|p{1in}|p{1.3in}|p{1in}|}
\hline
Term & Frequency (TF) & Document Frequency (DF) & Inverted Document Frequency (IDF) & TF-IDF score\\
\hline
Exponential & 4 & 15 & 0.824 & 3.296\\
\hline
Occurrence & 1 & 20 & 0.699 & 0.699\\
\hline
Multitude & 1 & 40 & 0.398 & 0.398\\
\hline
Abstract & 100 & 100 & 0 & 0\\
\hline
\end{tabular}
\caption{Example of TF-IDF score calculation.}\label{table:TFIDFScore}
\end{center}
\end{table}
\FloatBarrier
\end{jumpin}
As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.

\subheader{Validation methods}
The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through various validation metrics, one of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric}. The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization. These tasks can be designed to produce a score that indicates the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, findings about the performance of an embedding method are limited to the task on which they are tested. Their results cannot be generalized to state that the embeddings are overall "performing well". Validation tasks use either labeled or unlabeled data. Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data. Labeled data enables the use of unsupervised learning models since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration. Unlabelled data, on the other hand, requires human interaction to give a score for the produced result. The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.

@@

A classification validation method is a simple task which assigns a label to a text. \citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate. In their setup, the text was a pair of texts, and their categories were duplicate and non-duplicate. \citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie reviews. They validated their proposed paragraph vector model by determining whether a review was positive or negative. We will use the classification task for this research too, we will use journals (collection of articles) as classes, and the articles as items that need to be classified. We create a list, sorted on the similarity between article and journal, of journals for each article to get a measurable result from this. From this list we can extract, among other things, the position (rank) of the journal from which the article was taken.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings. The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain-specific embeddings are trained on a collection of texts that uses uncommon English (i.e., domain-specific terms) or is limited to a small number of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus. Figure~\ref{figure:domainPlot} illustrates our corpus, marked in green, in comparison to the Wikipedia corpus, marked in blue. Our corpus is a collection of domain specific texts, written in academic language. A set that would be more specific would only focus on the individual domains or sub-domains.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/domain_specification_graph}
\caption{Illustration of generic texts and domain specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
\end{figure}
